The Weakly Nonlinear Magnetorotational Instability in a local geometry

### 2017-03-22 paper/thingap_ref_response/thingap_mri_paper_ref_response_apj.tex
more text edits around figures

@@

\edit1{We analyze the average energy and angular momentum transport in the simulation domain (Figure \ref{fig:sim_theory_energy_jdot}).  }

>>>>

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{thingap_stressfig_Pm_1E-2}
\caption{\edit1{Total (Reynolds + Maxwell) stress in the domain as predicted from the weakly nonlinear theory.}} \label{fig:wnl_stress}
\end{figure}

@@

\edit1{We analyze the average energy and angular momentum transport in the simulation domain (Figure \ref{fig:sim_theory_energy_jdot}). We find good agreement between the theory and simulation values, especially considering that the weakly nonlinear theory applies rigorously to a channel of infinite height, while the simulation was carried out in a box with a vertical extent of only two critical wavelengths. Further comparisons between simulation and theory, including an analysis of the effect of the box height on the simulated flow, is deferred to future work. }
